Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-04-06 doc/Papers/IQS_convergence/cover-letter-iqs.tex
cover

In this paper, we revisit the improved quasi-static method (IQS) for its application to high order time discretizations and temperature feedback dynamics. We derive the IQS and IQS predictor-corrector method (IQS-PC) with the semi-analytical treatment of delayed neutron precursors and adiabatic heat-up. Temperature computation and feedback are treated on a separate time scale from shape and amplitude to increase the efficiency of nonlinear quasi-static process.

We show numerical results from four different test cases where we compare error from IQS computation and typical implicit discretization of the flux equation. A one-dimensional test was constructed to analyze error and nonlinear iteration convergence for IQS with up to fourth-order backward-difference-formulae discretization. IQS was applied to the TWIGL benchmark to show its performance with step doubling time adaptation. Analysis of the quasi-static treatment of temperature feedback are shown with results from the LRA benchmark and a test case from a model of the Transient Reactor Testing Facility.

IQS and IQS-PC were implemented into the MOOSE-Rattlesnake framework at Idaho National Laboratory in order to compute the results from the multi-dimensional examples.

>>>>

In this paper, we revisit the improved quasi-static method (IQS) for its application to high-order time discretizations and temperature feedback dynamics. We derive the IQS and IQS predictor-corrector method (IQS-PC) with the semi-analytical treatment of delayed neutron precursors and adiabatic heat-up. Temperature computation and feedback are treated on a separate time scale from the neutronic shape and amplitude functions to increase the efficiency of nonlinear quasi-static process.

We show numerical results from four different test cases where we compare error norms from IQS computation and standard implicit discretization of the flux equations. A one-dimensional test was constructed to analyze error and nonlinear iteration convergence for IQS with up to fourth-order backward-difference-formulae discretization. IQS was applied to the TWIGL benchmark to show its performance with step doubling time adaptation. Analysis of the quasi-static treatment of temperature feedback are shown with results from the LRA benchmark and a test case from a model of the Transient Reactor Testing Facility (TREAT).

IQS and IQS-PC were implemented into the MOOSE-Rattlesnake framework of Idaho National Laboratory.
